A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-06-13 paper/paper.tex

A small Python program (available on request) was created to examine each manifold in the census and compute its diameter. See Figure \ref{fig:type_statistics} for a plot of the number of manifolds by topological type and diameter. As claimed, every manifold with diameter greater than $J$ is a 3-sphere. The corresponding data using the coarser-grained edge-diameter can be found in Figure \ref{fig:type_statistics_edges}. Note the existence of $3$-manifolds with edge-diameter greater than half the maximum allowed edge-diameter and which are {\em not} homeomorphic to the 3-sphere. In particular, there are positively curved combinatorial 3-manifolds homeomorphic to $\mathbb{RP}^3$, $L(3,1)$ and $L(4,1)$ which have edge-diameter three.

@@

\section{Discussion}
Why does adding additional paths above and beyond edge-paths restore the classical structure to our proof?

>>>>

A small Python program (available on request) was created to examine each manifold in the census and compute its diameter and edge-diameter. See Figure \ref{fig:type_statistics} for a plot of the number of manifolds by topological type and diameter. As claimed, every manifold with diameter greater than $J$ is a 3-sphere. The corresponding data using the coarser-grained edge-diameter can be found in Figure \ref{fig:type_statistics_edges}. Note the existence of $3$-manifolds with edge-diameter greater than half the maximum allowed edge-diameter and which are {\em not} homeomorphic to the 3-sphere. However, we still have the following:

@@

\section{Discussion}
In the classical version of the generalized sphere theorem, the diameter bound is sharp and exactly half the maximum diameter allowed by the classical Bonnet-Myers theorem. In the discrete setting discussed in this paper, we have seen that this relationship between diameter bounds cannot be maintained if distances are measured by edge-paths. However, if we expand the set of paths to include hops and jumps then we can prove a discrete generalized sphere theorem using a sharp diameter bound exactly half that of our discrete Bonnet-Myers theorem.
